\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-12 manuscript.Rmd
Updates

```{r dependencymanager, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(warning = F, error = F, message = F)
library(packrat)
packrat::init()
#Only use when you have added some pack
#packrat::snapshot(ignore.stale=TRUE)

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 6.5, height = 1, 
                fixedsize = true, fontsize = 18 ]
                    6[label = '6-Factor  one factor with only two salient loadings']
                    7[label = 'Rejected']
                    }

@@

>>>>

```{r dependencymanager, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(warning = F, error = F, message = F)
set.seed(123)
```

```{undefined eval=FALSE, include=FALSE}
library(packrat)
packrat::init()
#Only use when you have added some pack
packrat::snapshot(ignore.stale=TRUE)

@@

                    4[label = 'Confirmatory Factor Analysis 
                     on the Five Factor Model (23 Items; N=262)
                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
                    }
                subgraph cluster_2 {
                      graph[fontname = Helvetica,shape = rectangle]
                      style = rounded
                     node[fontname = Helvetica, margin = 0.2,width = 8, height = 1, 
                fixedsize = true, fontsize = 18 ]
                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
                    7[label = 'Rejected']
                    }

@@

```{r MinVar, eval=FALSE, include=FALSE}
# ScreePlot with minimum variance explained, message=FALSE, warning=FALSE}
library(FactoMineR)
library(factoextra)
#PCA graph of variables
pca = PCA(EFA.data)
#Component ploted against percentage of explained variables
fviz_eig(pca, addlabels = T, max.overlaps = Inf)
```
